### 2017-03-24 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Final gas burner report edits that weren't pushed previously

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note XXXX}
\end{flushright}

@@

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
\endgroup
}

@@

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup

@@

\large
\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (February 2017) \\
CODEN: NTNOEF }

@@

\begingroup
{\bf This publication is available free of charge from:}
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{\bf http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup

>>>>

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note 1953}
\end{flushright}

@@

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1953}{http://dx.doi.org/10.6028/NIST.TN.1953}
\endgroup
}

@@

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1953}{http://dx.doi.org/10.6028/NIST.TN.1953} \\
\endgroup

@@

\large
\flushright{\bf National Institute of Standards and Technology Technical Note 1953 \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~1953, \pageref{LastPage} pages (February 2017) \\
CODEN: NTNOEF }

@@

\begingroup
{\bf This publication is available free of charge from:}
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1953}{\bf http://dx.doi.org/10.6028/NIST.TN.1953} \\
\endgroup
